\pkg{casebase}: An Alternative Framework For Survival Analysis

### 2020-02-06 analysis/paper/paper.Rmd
add discussion of flexible sampling

In future versions of the package, we also want to increase the complement of diagnostic and inferential tools that are currently available. For example, we would like to include the ability to compute confidence intervals for the cumulative incidence curve. The delta method or parametric bootstrap are two different strategies we can use to construct approximate confidence intervals. Furthermore, we would like to include functions to compute calibration and discrimination statistics (e.g. Brier score, AUC) for our models. Saarela and Arjas [-@saarela2015non] also describe how to obtain a posterior distribution for the AUC from their model. Their approach could also be included in \pkg{casebase}.

>>>>

In future versions of the package, we also want to increase the complement of diagnostic and inferential tools that are currently available. For example, we would like to include the ability to compute confidence intervals for the cumulative incidence curve. The delta method or parametric bootstrap are two different strategies we can use to construct approximate confidence intervals. Furthermore, we would like to include functions to compute calibration and discrimination statistics (e.g. Brier score, AUC) for our models. Saarela and Arjas [-@saarela2015non] also describe how to obtain a posterior distribution for the AUC from their model. Their approach could also be included in \pkg{casebase}. Finally, we want to provide more flexibility in how the case-base sampling is performed. This could be achieved by adding a \code{hazard} argument to the function \code{sampleCaseBase}. In this way, users could specify their own sampling mechanism. For example, they could provide a hazard that gives sampling probabilities that are proportional to the cardiovascular disease event rate given by the Framingham score [@saarela2015non].

### 2020-02-06 analysis/paper/paper.tex
add discussion of flexible sampling

In future versions of the package, we also want to increase the
complement of diagnostic and inferential tools that are currently
available. For example, we would like to include the ability to compute
confidence intervals for the cumulative incidence curve. The delta
method or parametric bootstrap are two different strategies we can use
to construct approximate confidence intervals. Furthermore, we would
like to include functions to compute calibration and discrimination
statistics (e.g.~Brier score, AUC) for our models. Saarela and Arjas
\citeyearpar{saarela2015non} also describe how to obtain a posterior
distribution for the AUC from their model. Their approach could also be
included in \pkg{casebase}.

@@

This report was generated on 2020-02-05 17:43:41 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> Local:    intro /home/turgeonm/Documents/git_repos/cbpaper
#> Head:     [c926a9e] 2020-01-21: Merge pull request #15 from sahirbhatnagar/fix-casebase-dependency
\end{CodeOutput}
\end{CodeChunk}

>>>>

In future versions of the package, we also want to increase the
complement of diagnostic and inferential tools that are currently
available. For example, we would like to include the ability to compute
confidence intervals for the cumulative incidence curve. The delta
method or parametric bootstrap are two different strategies we can use
to construct approximate confidence intervals. Furthermore, we would
like to include functions to compute calibration and discrimination
statistics (e.g.~Brier score, AUC) for our models. Saarela and Arjas
\citeyearpar{saarela2015non} also describe how to obtain a posterior
distribution for the AUC from their model. Their approach could also be
included in \pkg{casebase}. Finally, we want to provide more flexibility
in how the case-base sampling is performed. This could be achieved by
adding a \code{hazard} argument to the function \code{sampleCaseBase}.
In this way, users could specify their own sampling mechanism. For
example, they could provide a hazard that gives sampling probabilities
that are proportional to the cardiovascular disease event rate given by
the Framingham score \citep{saarela2015non}.

@@

This report was generated on 2020-02-06 13:51:22 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> Local:    intro /home/turgeonm/Documents/git_repos/cbpaper
#> Head:     [92cad64] 2020-02-05: add intro and edit some of the sections
\end{CodeOutput}
\end{CodeChunk}
